Efficient Machine Learning Approaches for Fast Risk Evaluation of VAs

### 2025-01-03 pre_private/pre.tex
11

\begin{frame}{Nested Simulation for VAs}

@@

>>>>

\begin{frame}{Nested Simulation for Risk Management of VAs}

@@

\begin{frame}{Standard Nested Simulation for VAs}

Standard nested simulation for VAs is similar to the one for options.

\begin{itemize}
    \item Generate $M$ outer scenarios
    \item For each outer scenario,
    \begin{itemize}
        \item Perform $N$ inner simulations
        \item Estimate hedging loss $L_i$ with $\hat{L}_i$
    \end{itemize}
    \item Use estimated losses to calculate tail risk measures (e.g., $95\%$-CVaR)
\end{itemize}

\textbf{Main challenge:}
\begin{itemize}
    \item Computational budget is limited.
    \item Accuracy of the estimation depends on both $M$ and $N$.
\end{itemize}

\begin{frame}{Two-Stage LSTM-based Nested Simulation for VAs}
